### 2024-04-01 doc/sections/mav-mechanisation.tex
Minor fixes

We did not attempt to formalise the syntactic proof of generalised
cut-elimination directly. We suspect that this would likely be
extremely involved due to the widespread and implicit use of syntactic
equalties when manipulating formulas, as well as the construction of
the relevant termination measures. The semantic constructions are
relatively straightforward to formalise in Agda.

>>>>

We did not attempt to formalise the syntactic proof of generalised
cut-elimination directly. We suspect that this would likely be
extremely involved due to the widespread and implicit use of syntactic
equalities when manipulating structures, as well as the construction of
the relevant termination measures. The semantic constructions are
relatively straightforward to formalise in Agda.
